Distributed computation of linear algebra operations

### 2023-10-30 latex/presentation/main.tex
inverse presentation

\begin{frame}[fragile]{Determinant with Ray (Serial)}
    \begin{lstlisting}[language=Python]
def det(self):
if self.is_square():
    size = self.size()["rows"]
    a = self.get()

@@

\begin{frame}[fragile]{Determinant with Ray (minor)}
    The \textit{minor} function
    \begin{lstlisting}[language=Python]
    def minor(self, i, j):
    '''
    Extract a minor matrix by removing the ith row and jth column
    '''

@@

\begin{frame}[fragile]{Determinant with Ray (dist\_minor)}
    \begin{lstlisting}[language=Python]
@ray.remote
def dist_minor(A, i, j):
    '''
    Extract a minor matrix by removing the ith row and jth column
    '''

@@

\begin{frame}[fragile]{Determinant with Ray (Parallel)}

@@

\begin{frame}[fragile]{Inverse with Ray}
    \begin{lstlisting}[language=Python]
            codice inversa
        \end{lstlisting}
\end{frame}

@@

\begin{frame}[fragile]{Rank with Ray}
    \begin{lstlisting}[language=Python]
            codice rango
        \end{lstlisting}
\end{frame}

>>>>

\begin{frame}[fragile]{Determinant function (Serial)}
    \begin{lstlisting}[language=Python]
def det(self):
if self.is_square():
    size = self.size()["rows"]
    a = self.get()

@@

\begin{frame}[fragile]{Determinant function (minor)}
    The \textit{minor} function
    \begin{lstlisting}[language=Python]
    def minor(self, i, j):
    '''
    Extract a minor matrix by removing the ith row and jth column
    '''

@@

\begin{frame}[fragile]{Determinant function (dist\_minor)}
    \begin{lstlisting}[language=Python]
@ray.remote
def dist_minor(A, i, j):
    '''
    Extract a minor matrix by removing the ith row and jth column
    '''

@@

\begin{frame}[fragile]{Determinant function (Parallel)}

@@

\begin{frame}[fragile]{Inverse function (Serial) (1)}
    \begin{lstlisting}[language=Python]
def inv(self):
if not self.is_square():
    raise Exception("Matrix must be square")

elif self.det() == 0:
    raise Exception("Matrix is not invertible")

else:
    rows, cols = self.shape()
    data = self.get()

    det = self.det()

    # special case for 2x2 matrix:
    if rows == cols == 2:
        return [[data[1][1] / det, -1 * data[0][1] / det],
                [-1 * data[1][0] / det, data[0][0] / det]]

...
        \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{Inverse function (Serial) (2)}
    \begin{lstlisting}[language=Python]
...
    # find matrix of cofactors
    cof_matrix = []

    for row in range(rows):
        cof_row = []

        for column in range(cols):
            minor = self.minor(row, column)

            cof_row.append(((-1)**(row + column)) * minor.det())

        cof_matrix.append(cof_row)

    cof_matrix = Matrix(cof_matrix).transpose()

    cof_rows, cof_cols = cof_matrix.shape()
    cof_data = cof_matrix.get()

    for row in range(cof_rows):
        for column in range(cof_cols):
            cof_data[row][column] = cof_data[row][column] / det

    return cof_matrix
        \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{Distributing the inverse function}
    To distribute the inverse function we will need two auxiliary functions: \textit{inv\_cof\_matrix} and \textit{inv\_calc}
\end{frame}

\begin{frame}[fragile]{inv\_cof\_matrix}
    Find all the cofactor matrices of a given matrix
    \begin{lstlisting}[language=Python]
@ray.remote
def inv_cof_matrix(A, row, cols):
    from matrix import Matrix

    cof_row = []
    minor_futures = [Matrix.dist_minor.remote(A, row, col) for col in range(cols)]
    minors = ray.get(minor_futures)

    for col,minor in zip(range(cols), minors):
        cof_row.append(((-1)**(row + col)) * minor.det())

    return cof_row
        \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{inv\_calc}
    Calculation step for the main function
    \begin{lstlisting}[language=Python]
@ray.remote
def inv_calc(row, cof_cols, cof_data, det):
    for col in range(cof_cols):
        return (row, col, (cof_data[row][col] / det))
        \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{Inverse function (Parallel) (1)}
    \begin{lstlisting}[language=Python]
def inv(self):
if not self.is_square():
    raise Exception("Matrix must be square")

elif self.det() == 0:
    raise Exception("Matrix is not invertible")

else:
    rows, cols = self.shape()
    data = self.get()
    det = self.det()

    # special case for 2x2 matrix:
    if rows == cols == 2:
        m = [[data[1][1] / det, -1 * data[0][1] / det],
                [-1 * data[1][0] / det, data[0][0] / det]]

        return Matrix([[round(i, 8) for i in j] for j in m])
...    
            \end{lstlisting}
\end{frame}

\begin{frame}[fragile]{Inverse function (Parallel) (2)}
    \begin{lstlisting}[language=Python]
...
    # find matrix of cofactors
    cof_rows_futures = [t.inv_cof_matrix.remote(self, row, cols) for row in range(rows)]
    cof_matrix = ray.get(cof_rows_futures)
    cof_matrix = Matrix(cof_matrix).transpose()

    cof_rows, cof_cols = cof_matrix.shape()
    cof_data = cof_matrix.get()

    data_futures = [t.inv_calc.remote(row, cof_cols, cof_data, det) for row in range(cof_rows)]

    for data in ray.get(data_futures):
        for row, col, value in [data]:
            cof_data[row][col] = value

    return Matrix([[round(i, 8) for i in j] for j in cof_matrix])
            \end{lstlisting}
\end{frame}

@@

\begin{frame}[fragile]{Rank function}
    \begin{lstlisting}[language=Python]
            codice rango
        \end{lstlisting}
\end{frame}
